Palmer amaranth (*Amaranthus palmeri*) adaptation to agroecossystems

### 2021-08-10 Manuscript/Manuscript.Rmd
as

>>>>

Palmer amaranth gender was fitted to a binary logistic regression [@bangdiwala2018]. Binary logistic regression is used for predicting binary classes, such gender of Palmer amaranth plants. The whole dataset was splitted into 80% train and 20% test data. The 80% train is used for the model training and the rest 20% is used for checking how the model generalized on unseen dataset. With 80% dataset, a binary response variable, male (0) and female (1), was fitted to a generalized linear model (*glm* function) including day of year harvest, height, weight, crop and month as independent variables. The model family was binomial with a logit function. The model fit was assessed through pseudo R squared values (McFadden, Cox and Snell, Cragg and Uhler) and likelihood ratio using *nagelkerke* function ("rcompanion" package). The marginal effects computation was performed with Average Marginal Effects at every observed value of x and average across the results (AMEs) [@leeper2017] using *margins* function from "margins" package. The rest 20% dataset was predicted using *predict* function with a cutoff estimation for male or female using *performance* function.
